Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-12-17 manuscript.tex
round 2 comment on weak/strong links

    Correspondence concerning this article should be addressed to Masoud
    Jasbi, Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA,
    94305-2150. E-mail:
    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoud_jasbi@fas.harvard.edu}}
  }

@@

>>>>

    Correspondence concerning this article should be addressed to Masoud
    Jasbi, Department of Linguistics, Boylston Hall, Cambridge, MA,
    94305-2150. E-mail:
    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoud_jasbi@fas.harvard.edu}}
  }

@@

\change{We should add that researchers may vary with respect to which linking hypothesis (weak vs. strong) they consider more plausible. Many researchers would argue for the weak link. For them, judgments fall into three theoretically motivated categories: false, true but infelicitous, true and felicitous. Therefore, it is reasonable that false and true+felicitous responses occupy the ends of the scale while true-infelicitous responses occupy the mid-portion. In critical trials, participants judge underinformative statements that are true but infelicitous and therefore the mid portion of the scale can provide evidence for implicature computation. However, some other researchers argue that a strong link provides the best evidence for implicatures. They argue that if a participant computes an inference that results in an implicature-rich interpretation, their response in the task should show the commitment to the interpretation by judging the underinformative utterance as false or wrong. Any other response shows that they have not truly computed an implicature; i.e. they are not committed to the inference. So far these discussions have remained largely informal. In this paper we stay neutral with respect to the plausibility of each link and only aim to demonstrate the consequences of assuming them.}
